---
title: "Organization Cleaning"
format: html
editor: visual
---

## Organizations

Structure of old organization data:

"Organization" "Address" "County" "Sector" "Type" "lon" "lat" "county_name" "lat_c" "long" "search"

```{r}
library(tidyverse)
library(janitor)
library(readxl)
library(sf)
library(leaflet)
library(reactable)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```

You can add options to executable code like this

```{r}
#| echo: false

orgs_raw <- read_excel("orgs_master.xlsx") |> 
  clean_names()

  met_pallete_geo <- MetBrewer::met.brewer(name="Isfahan2",n=20)
  met_pallete_geo <- as.character(met_pallete_geo)
  
reactable(orgs_raw)
```

## Map

```{r, mapview}

pal =       colorFactor(
  palette = met_pallete_geo,
  reverse = FALSE,
  domain = orgs_raw$type,
  na.color = rgb(0, 0, 0, 0)
)
  
# create map widget with OpenStreetMap tile
map <- leaflet(orgs_raw) %>%
  addTiles() %>%
  addCircleMarkers(
    lng =  ~ longitude,
    lat =  ~ latitude,
    color = ~ type,
    fillColor = ~ pal(type),
    fillOpacity = .7,
    popup =  ~ organization
  ) %>%
  addLegend('bottomright', pal=pal, values = ~type)

# print map widget
map

```

## Types

```{r}
unique(orgs_raw$type)
```

## Subcategories

-   water and treatment providers

    -   CO, City

-   regulators and monitors

-   NGO and government Researchers

    -   NGO

-   Water body and/or land manager

    -   CRD, DD,

It's real unclear what everything is.....

```{r sub}
subs <- orgs_raw

subs <- subs |> 
  mutate(sector = case_when(
    type == "NGO" ~ "NGOs and Researchers",
    type == "CO" ~ "Water and Treatment Provider",
    TRUE ~ ""
  ))



```
